---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center"
)
```


# lpirfs
An R-package which estimates linear and non-linear impulse responses
with local projections by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518).

## Main features

- Estimate linear and non-linear impulse responses with local projections.
- Functions to plot linear and non-linear impulse responses.
- Functions are partly implemented in *Rcpp* and *RcppArmadillo* to improve efficiency.
- High performance with parallel computation.

## Installation

You can install the released version of **lpirfs** from [CRAN](https://CRAN.R-project.org):

```{r, eval = FALSE}
install.packages("lpirfs")
```

And the development version from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("AdaemmerP/lpirfs")
```
## Example: Linear impulse responses
Load libraries:
```{r, message = FALSE }
# Load packages
  library(dplyr)
  library(doSNOW)
  library(parallel)
  library(vars)
  library(Rcpp)
  library(lpirfs)
```

Load data set from package to estimate a simple, new-Keynesian, closed-
economy model. These data are used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV. 
Please see the data's help file or the original paper for a detailed description. 
```{r, message = FALSE }
# Load data (from package)
  data_set_df <- interest_rules_var_data
```

Make list and specify input variables to estimate linear impulse responses. 
```{r, message = FALSE }
# Make list for inputs
  specs <- list()

# Specify inputs
  specs$lags_lin       <- 4L      # Number of lags
  specs$lags_criterion <- NaN     # Lag length criterion (AICc, AIC or BIC)
  specs$max_lags       <- NaN     # If lags_criterion is chosen, set maximum number of lags  
  specs$trend          <- 0L      # 0 = no trend, 1 = trend, 2 = trend and quadratic trend
  specs$shock_type     <- 1L      # 0 = standard deviation shock, 1 = unit shock
  specs$confint        <- 1.96    # Width of confidence bands: 1 = 68%, 1.67 = 90%, 1.96 = 95%
  specs$hor            <- 12L     # Length of horizon
```
Estimate linear impulse responses. 
```{r, message = FALSE }  
  results_lin  <- lp_lin(data_set_df, specs)
```

Make plots for impulse responses of linear model.
```{r, message = FALSE }
  linear_plots <- plot_lin_irfs(results_lin)
```
Display single impulse responses: 

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable in (GDP_gap). 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (Inflation). 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
  linear_plots[[1]]
  linear_plots[[2]]
```

Display all plots:

- This graph is similar to Figure 5 in Jordà (2005), p. 176, but has slightly wider confidence bands. 
- Figure 5 in Jordà (2005) is replicated when specs$confint = 1.67 (90% error bands).
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }  
# Show all plots
  library(ggpubr)
  library(gridExtra)

  lin_plots_all <- sapply(linear_plots, ggplotGrob)
  marrangeGrob(lin_plots_all, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top=NULL)
```

## Example: Non-linear impulse responses
Load libraries:
```{r, message = FALSE }
# Load packages
  library(dplyr)
  library(doSNOW)
  library(parallel)
  library(Rcpp)
  library(lpirfs)
  library(mFilter)
  library(vars)
```

Load data set from package to estimate a non-linear, new-Keynesian, closed-
economy model. This data set is used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV.
Please see the data's help file or the original paper for a detailed description. 
```{r, message = FALSE }
# Load data (from package)
  data_set_df <- interest_rules_var_data
```

Make list and specify input variables to estimate non-linear impulse responses. 
```{r, message = FALSE }
# Make list for inputs
  specs <- list()

# Specify inputs
  specs$lags_nl        <- 3L      # Number of lags
  specs$lags_criterion <- NaN     # Lag length criterion (AICc, AIC or BIC)
  specs$max_lags       <- NaN     # If lags_criterion is chosen, maximum number of lags  
  specs$trend          <- 0L      # 0 = no trend, 1 = trend, 2 = trend and quadratic trend
  specs$shock_type     <- 1L      # 0 = standard deviation shock, 1 = unit shock
  specs$confint        <- 1.96    # Width of confidence bands: 1 = 68%, 1.67 = 90%, 1.96 = 95%
  specs$hor            <- 12L     # Length of horizon
```

Provide a switching variable to separate the data into two regimes.
```{r, message = FALSE }
# Specifications for switching variable
  specs$switching      <- data_set_df$GDP_gap # The output gap is used to differentiate between two regimes
  specs$hp_filter      <- 1                   # 0 = Do not use HP-filter to decompose switching-variable, 
                                              # 1 = Use HP-filter to decompose switching-variable
  specs$lambda         <- 1600                # Monthly = 129600, Quarterly = 1600, Annual = 6.25
  specs$gamma          <- 3                   # Numeric value > 0
```

The switching variable ($z$) is either decomposed by the Hodrick-Prescott filter (*specs$hp_filter = 1*) or directly plugged into the follwing switching function.


 -  $F({z_t}) \ = \  exp(-\gamma \ z_t)/(1 + exp(-\gamma \ z_t))$
   
The lagged exogenous variables ($X_{t-p}$) are then multiplied with the values of the transition function at *t − 1* where 

- Regime 1: $X_{t-p}*(1-F(z_{t-1}))$,
- Regime 2: $X_{t-p}*F(z_{t-1})$.


IMPORTANT:The index of $z$ is set to *t − 1* to avoid contemporaneous feedback (see 
[Auerbach and Gorodnichenko; 2012](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1) for details). 
The lag is created  automatically in *create_nl_data* of the package. 
If you do not want that the exogenous variables are multiplied with lagged values of $F({z_t})$, you have to provide the switching variable with a lead of one.


Estimate non-linear impulse responses. 
```{r, message = FALSE }  
  results_nl <- lp_nl(data_set_df, specs)
```

Save values from transition function.
```{r, message = FALSE } 
  fz      <- results_nl$fz
```

Plot output gap
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE } 
# Make date sequence. Start in October because the non-linear model is estimated with three lags.
  dates   <- seq(as.Date("1955/10/1"), as.Date("2003/1/1"), by = "quarter")
  data_df <- data_frame(x = dates, fz = fz, gdp_gap = specs$switching[(specs$lags_nl+1):length(data_set_df$FF)])

# Plot  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = gdp_gap)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```

Plot tranistion function
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE }  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = fz)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```

Create and save all plots.
```{r, message = FALSE }
    nl_plots <- plot_nl_irfs(results_nl)
```

Show first impulse response of each regime: 

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable (GDP_gap) in regime 1. 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (Inflation) in regime 2. 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
# Load packages
  library(ggpubr)
  library(gridExtra)

# Save plots based on states
  s1_plots <- sapply(nl_plots$gg_s1, ggplotGrob)
  s2_plots <- sapply(nl_plots$gg_s2, ggplotGrob)

  plot(s1_plots[[1]])
  plot(s2_plots[[2]])
```

Show all impulse responses of regime 1.
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s1_plots, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top =  NULL)
```

Show all impulse responses of regime 2.
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s2_plots, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top = NULL)
```


## References
* Auerbach, A. J., and Gorodnichenko Y. (2012). "Measuring the Output Responses to Fiscal Policy." *American Economic Journal: Economic Policy*, 4    (2):   1-27. [doi:10.1257/pol.4.2.1](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)

* Jordà, O. (2005) "Estimation and Inference of Impulse Responses by Local Projections." *American Economic Review*, 95 (1): 161-182.
[doi:10.1257/0002828053828518](https://www.aeaweb.org/articles?id=10.1257/0002828053828518)

* Newey W.K., and West K.D. (1987). “A Simple, Positive-Definite, Heteroskedasticity and Autocorrelation Consistent Covariance Matrix.” *Econometrica*, 55, 703–708. [doi:10.2307/1913610](https://www.jstor.org/stable/1913610?seq=1#page_scan_tab_contents)

* Ramey, V.A., and Zubairy, S. (2018). "Government Spending Multipliers in Good Times and in Bad: Evidence from US Historical Data." Journal of        Political Economy, 126 (2), 850-901. [doi:10.1086/696277](https://www.journals.uchicago.edu/doi/10.1086/696277)

## Acknowledgements
I greatly benefitted from the profound *R* and *Rcpp* knowledge of [Philipp Wittenberg](https://github.com/wittenberg). I am also grateful to [Sarah Zubairy](https://sites.google.com/site/sarahzubairy/) for sending me the *Matlab* code before the publication their [paper](https://www.journals.uchicago.edu/doi/10.1086/696277).

## Development
I am currently working on a function to include exogenous variables to give a matrix as input for the shock identification. 

### Author
Philipp Adämmer

### License

GPL (>= 2)
