---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# lpirfs

An R-package which estimates linear and non-linear impulse responses
with local projections by Jordà (2005).

## Main features

- Linear impulse responses with local projections
- Non-linear impulse responses with local projections
- Functions to plot impulse responses

## Installation

You can install the released version of **lpirfs** from [CRAN](https://CRAN.R-project.org) 
or from github:

```{r, eval = FALSE}
install.packages("lpirfs")
# install.packages("devtools")
devtools::install_github("AdaemmerP/lpirfs")
```

## Example: Linear impulse responses
Load libraries:
```{r, message = FALSE }
# Load packages
  library(dplyr)
  library(doSNOW)
  library(parallel)
  library(Rcpp)
  library(lpirfs)
```

Load data set from package 
```{r, message = FALSE }
# Load data (from package)
  data_set_df <- interest_rules_var_data
```

Make list for input 
```{r, message = FALSE }
# Create list for input
  specs <- list()

# Specify inputs
  specs$lags_lin       <- 4L
  specs$lags_criterion <- NaN
  specs$max_lags       <- 2L
  specs$trend          <- 0L
  specs$shock_type     <- 1L
  specs$confint        <- 1.96
  specs$hor            <- 12L
```
Make list for input 
```{r, message = FALSE }  
# Estimate model 
  results_lin  <- lp_lin(data_set_df, specs)
```

```{r, message = FALSE }
# Make plots
  linear_plots <- plot_lin_irfs(results_lin)


# Show single plots
  linear_plots[[1]]
  linear_plots[[2]]

# Show all plots
  library(ggpubr)
  library(gridExtra)

  lin_plots_all <- sapply(linear_plots, ggplotGrob)
  marrangeGrob(lin_plots_all, nrow = ncol(data_set_df), ncol = ncol(data_set_df))
```
