---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center"
)
```


# lpirfs
An R-package which estimates linear and non-linear impulse responses
with local projections by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518).

## Main features

- Estimate linear and non-linear impulse responses with local projections.
- Functions to plot linear and non-linear impulse responses.
- Functions are partly implemented in *Rcpp* and *RcppArmadillo* to improve efficiency.
- High performance with parallel computation.

## Installation

You can install the released version of **lpirfs** from [CRAN](https://CRAN.R-project.org):

```{r, eval = FALSE}
install.packages("lpirfs")
```

or the development version from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("AdaemmerP/lpirfs")
```
## Examples
Examples can be found [here.](https://adaemmerp.github.io/lpirfs/README_docs.html)

## Acknowledgements
I greatly benefitted from the profound *R*, *Rcpp* and *Github* knowledge of [Philipp (stack) Wittenberg](https://github.com/wittenberg) and [Detlef (overflow) Steuer](https://github.com/dsteuer). All errors are obviously mine. 

## Development
I am working on a function to include exogenous variables and a function which allows to manually
identify the linear combinations of the reduced form residuals. 

### Author
Philipp Adämmer

### License

GPL (>= 2)
