---
output: html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "pics_docs/",
  fig.align = "center"
)
```

## This page gives examples and replicates empirical results to show how to use the R-package *lpirfs*.

### Example: Linear impulse responses with local projections
Load library:
```{r, message = FALSE }
  library(lpirfs)
```

Load data from package to estimate a simple, new-Keynesian, closed-economy 
model. These data are used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV, p. 174. 
See the data's help file in the package or the [paper](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) for a detailed description on the data. 
```{r, message = FALSE }
  endog_data <- interest_rules_var_data
```

Estimate linear impulse responses with function *lp_lin*. Note that the endogenous and exogenous data have to be 
a data.frame. 
```{r, message = FALSE }  
results_lin <- lp_lin(endog_data, 
                           lags_endog_lin = 4,   # Number of lags for endogenous data
                           lags_criterion = NaN,  # Lag length criterion (AICc, AIC or BIC) or NaN
                           max_lags       = NaN,  # Maximum number of lags or NaN
                           exog_data      = NULL, # Exogenous data
                           lags_exog      = NULL, # Lags for exogenous data
                           contemp_data   = NULL, # Exogenous data with contemporaneous impact
                           trend          = 0,   # 0 = no trend, 1 = trend, 2 = trend & trend^2    
                           shock_type     = 1,   # 0 = standard deviation shock, 1 = unit shock
                           confint        = 1.96, # Width of confidence bands: 
                                                  # 1 = 68%, 1.67 = 90%, 1.96 = 95%
                           hor            = 24,  # Number of horizons for impulse responses
                           num_cores      = NULL) # Number of cores to use. When NULL, the number of cores is chosen 
                                                  # automatically    
```

Create plots for impulse responses of linear model with function *plot_lin*.
```{r, message = FALSE }
  linear_plots <- plot_lin(results_lin)
```
Display single impulse responses: 

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable (GDP_gap). 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (inflation). 
- ...
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
  linear_plots[[1]]
  linear_plots[[2]]
```

Display all plots (compare with Figure 5 in Jordà (2005), p. 176):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }  
# Load libraries to plot all impulse responses
# The package does not depend on those packages so they have to be installed
  library(ggpubr)
  library(gridExtra)

# Show all plots 
  lin_plots_all <- sapply(linear_plots, ggplotGrob)
  marrangeGrob(lin_plots_all, nrow = ncol(endog_data), ncol = ncol(endog_data), top = NULL)
```

### Example: Nonlinear impulse responses with local projections

Load data set from package to estimate a nonlinear, new-Keynesian, closed-economy 
model. These data are used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV, p.176. 
See the data's help file or the [paper](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) for a detailed description on the data. 
```{r, message = FALSE }
  endog_data <- interest_rules_var_data
```

$$ $$
The switching variable ($z_t$) can either be decomposed by the Hodrick-Prescott filter (see [Auerbach and Gorodnichenko, 2013](http://www.nber.org/papers/w17447.pdf)) or directly plugged into the following logistic function:  


 $$F({z_t})  = \  \frac{e^{(-\gamma z_t)}}{\left(1 + e^{(-\gamma z_t)}\right)},$$
 


where $\gamma > 0$. To differentiate between the two regimes, the exogenous variables ($\boldsymbol{y}_{t-p}$) are multiplied with the values of the transition function at *t − 1* where

- Regime 1 $(R_1)$: $\boldsymbol{y}_{t-i}\cdot(1-F(z_{t-1}))$,  $\qquad i = 1, ..., p$,

and

- Regime 2 $(R_2)$: $\boldsymbol{y}_{t-i}\cdot F(z_{t-1})$,  $\hskip 4.5em i = 1, ..., p$.

 IMPORTANT: The index of $z$ is set to *t − 1* in order to avoid contemporaneous feedback (see 
[Auerbach and Gorodnichenko 2012](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)). 
The lag is automatically created in the package function *create_nl_data*. 
If you do not want the exogenous variables to be multiplied with lagged values of $F({z_t})$, you have to provide the switching variable with a lead of one.

Nonlinear impulse responses are computed as in [Ahmed and Cassou (2016)](https://www.sciencedirect.com/science/article/pii/S0164070416300490). 
First, a reduced VAR is estimated to obtain the covariance matrix of the residuals $\Sigma$. The Cholesky decomposition is then applied to obtain the shock matrix with columns denoted by $d_j$. IRFs for both regimes are estimated via:

$$\hat{IR}^{R_1}(t,h,d_j) = \hat{\boldsymbol{B}}_{1, R_1}^h d_j, \ \ \ \ \ \ \ \ \ h = 1, ..., H, $$ 
and 

$$\hat{IR}^{R_2}(t,h,d_j) = \hat{\boldsymbol{B}}_{1, R_2}^h d_j, \ \ \ \ \ \ \ \ \ h = 1, ..., H, $$ 


with $\hat{\boldsymbol{B}}_{1, R1}^0 = I$ and $\hat{\boldsymbol{B}}_{1, R2}^0 = I$. The parameters are obtained by running a sequence of OLS forecasts (local projections):

$$ \boldsymbol{y}_{t+h} = \boldsymbol{\alpha}^h + \boldsymbol{B}_{1, R_1}^{h} \left(\boldsymbol{y}_{t-1}\cdot(1-F(z_{t-1})\right) \ + \ ...\ +\ 
    \boldsymbol{B}_{p, R_1}^{h} \left(\boldsymbol{y}_{t-p}\cdot(1-F(z_{t-1})\right) + \\
\hskip 7.6em \boldsymbol{B}_{1, R_2}^{h} \left(\boldsymbol{y}_{t-1}\cdot F(z_{t-1}\right)) \ + \ ... \  + \  \boldsymbol{B}_{p, R_2}^{h} \left(\boldsymbol{y}_{t-p}\cdot F(z_{t-1}\right)) + \boldsymbol{\varepsilon}_{t+h}^h,
$$
with $h = 1,..., H.$

$$ $$

Estimate nonlinear impulse responses with package function *lp_nl*. Note that the endogenous and exogenous data have 
to be a data.frame.
```{r, message = FALSE }  
results_nl <- lp_nl(endog_data, 
                        lags_endog_lin = 4,   # Number of lags for (reduced) linear VAR to obtain shock matrix. 
                        lags_endog_nl  = 4,   # Number of lags for nonlinear model. 
                        lags_criterion = NaN,  # Lag length criterion (AICc, AIC or BIC) or NaN.
                        max_lags       = NaN,  # If lags_criterion is chosen, maximum number of lags. 
                        exog_data      = NULL, # Exogenous data
                        lags_exog      = NULL, # Lags for exogenous data
                        contemp_data   = NULL, # Exogenous data with contemporaneous impact
                        trend          = 1,   # 0 = no trend, 1 = trend, 2 = trend & trend^2.
                        shock_type     = 0,   # 0 = standard deviation shock, 1 = unit shock.
                        confint        = 1.67, # Width of confidence bands: 
                                               # 1 = 68%, 1.67 = 90%, 1.96 = 95%.
                        hor            = 24,   # Length of horizon.
                        switching      = endog_data$Infl, # Inflation rate.
                        use_hp         = TRUE, # Use HP-filter? TRUE or FALSE.   
                        lambda         = 1600, # Ravn and Uhlig (2002):
                                               # Anuual data    = 6.25
                                               # Quarterly data = 1600
                                               # Monthly data   = 129,600
                        gamma          = 6,    # Numeric value > 0. 
                        num_cores      = NULL) # Number of cores to use. When NULL, the number of cores is chosen 
                                               # automatically    
```

Save values from transition function and list which contains data information. 
```{r, message = FALSE } 
  fz      <- results_nl$fz
  specs   <- results_nl$specs
```

Plot output gap.
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE } 
# Make date sequence and store data in a data.frame for ggplot.
  dates   <- seq(as.Date("1955/12/1"), as.Date("2003/1/1"), by = "quarter")
  data_df <- data.frame(x = dates, fz = fz, switch_var = specs$switching[(specs$lags_endog_nl+1):length(endog_data$FF)])

# Plot  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = switch_var)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```

Plot transition function.
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE }  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = fz)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```
Note that values close to one correspond to periods of low inflation rates (regime 2) and values close
zero correspond to periods of high inflation rates (regime 1).


Create and save all plots with function *plot_nl*
```{r, message = FALSE }
    nl_plots <- plot_nl(results_nl)
```

Show single impulse responses for each regime:

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable (GDP_gap) in regime 1. 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (Inflation) in regime 2. 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
# Load packages
# The package does not depend on those packages so they have to be installed
  library(ggpubr)
  library(gridExtra)

# Save plots based on states
  s1_plots <- sapply(nl_plots$gg_s1, ggplotGrob)
  s2_plots <- sapply(nl_plots$gg_s2, ggplotGrob)

  plot(s1_plots[[1]])
  plot(s2_plots[[2]])
```

Show all impulse responses of regime 1 (high inflation rates):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s1_plots, nrow = ncol(endog_data), ncol = ncol(endog_data), top =  NULL)
```

Show all impulse responses of regime 2 (low inflation rates):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s2_plots, nrow = ncol(endog_data), ncol = ncol(endog_data), top = NULL)
```

### Example: Linear impulse responses with instrument variable and local projections

This example replicates results from the Supplementary Appendix
by [Ramey and Zubairy (2018)](https://www.journals.uchicago.edu/doi/10.1086/696277) (RZ-18). 
They use local projections to re-evaluate findings in [Auerbach and Gorodnichenko (2012)](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)
(AG-12).

Load data which is included in the package and taken from [RZ-18](https://www.journals.uchicago.edu/doi/10.1086/696277).
```{r, message = FALSE }
 ag_data           <- ag_data
 sample_start      <- 8
 sample_end        <- dim(ag_data)[1]
 
# Endogenous variables
 endog_data        <- ag_data[sample_start:sample_end,3:5]
 
# Shock variable ('Instrument') 
 shock             <- endog_data[, 1]
```

Estimate model with constant and 4 lags.
```{r, message = FALSE }
 results_lin_iv <- lp_lin_iv(endog_data,
                         shock          = shock,
                         lags_endog_lin = 4,
                         exog_data      = NULL,
                         lags_exog      = NULL,
                         contemp_data   = NULL,
                         lags_criterion = NaN,
                         max_lags       = NaN,
                         trend          = 0,
                         confint        = 1.96,
                         hor            = 20,
                         num_cores      = NULL)

```
Make and save plots
```{r, message = FALSE }
 iv_lin_plots    <- plot_lin(results_lin_iv)
```
- The first element of 'iv_lin_plots' shows the response of the first
  variable (Gov) to the 'instrument-shock' (Gov).
- The second element of 'iv_lin_plots' shows the response of the second
  variable (Tax) to the 'instrument-shock' (Gov).
- ...

This plot equals the left plot in the mid-panel of Figure 12 in the Supplementary Appendix by 
RZ-18. 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
  iv_lin_plots[[1]]
```
Multiply the log output response by a conversion factor of ~5.6 (AG-12; RZ-18). 
```{r, message = FALSE }
GYsc            <- mean(exp(endog_data$GDP)/exp(endog_data$Gov))

multiplier_mean <- results_lin_iv$irf_lin_mean*GYsc
multiplier_up   <- results_lin_iv$irf_lin_up*GYsc
multiplier_low  <- results_lin_iv$irf_lin_low*GYsc

results_lin_iv  <- list(irf_lin_mean  = multiplier_mean,
                        irf_lin_up    = multiplier_up,
                        irf_lin_low   = multiplier_low,
                        specs         = results_lin_iv$specs)

# Make new plots 
 iv_lin_plots   <- plot_lin(results_lin_iv)
```
 
Compare with the right plot in the mid-panel of Figure 12 in the Supplementary Appendix by 
RZ-18. 

```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
iv_lin_plots[[3]]
```


## Example: Nonlinear impulse responses with instrument variable and local projections

Load data
```{r, message = FALSE }
 ag_data           <- ag_data
 sample_start      <- 7
 sample_end        <- dim(ag_data)[1]
 endog_data        <- ag_data[sample_start:sample_end, 3:5]
```

The shock variable ('instrument') is created by RZ-18 and available as supplementary data
to their paper. The government spending shock is included in the package.
```{r, message = FALSE }
 shock            <- as.data.frame(ag_data$Gov_shock_mean[sample_start:sample_end])
```

AG-12 include four lags of the 7-quarter moving average growth rate
as exogenous regressors in their model (see RZ-18).
```{r, message = FALSE }
 exog_data        <- as.data.frame(ag_data$GDP_MA[sample_start:sample_end])
```

AG-12 use the 7-quarter moving average growth rate as switching variable.
They adjust it to have suffiently long recession periods.
```{r, message = FALSE }
 switching_variable <- as.data.frame(ag_data$GDP_MA[sample_start:sample_end]) - 0.8
```



Estimate nonlinear model 
```{r, message = FALSE }
 results_nl_iv <- lp_nl_iv(endog_data,
                           lags_endog_nl     = 3,
                           shock             = shock,
                           exog_data         = exog_data,
                           lags_exog         = 4,
                           contemp_data      = NULL,
                           lags_criterion    = NaN,
                           max_lags          = NaN,
                           trend             = 0,
                           confint           = 1.96,
                           hor               = 20,
                           switching         = switching_variable,
                           use_hp            = FALSE,
                           lambda            = NaN,
                           gamma             = 3)

```

Multiply the log output responses by a conversion factor of ~5.6 (AG-12; RZ-18). 
```{r, message = FALSE }
GYsc            <- mean(exp(endog_data$GDP)/exp(endog_data$Gov))

irf_s1_mean <- results_nl_iv$irf_s1_mean*GYsc
irf_s1_up   <- results_nl_iv$irf_s1_up*GYsc
irf_s1_low  <- results_nl_iv$irf_s1_low*GYsc

irf_s2_mean <- results_nl_iv$irf_s2_mean*GYsc
irf_s2_up   <- results_nl_iv$irf_s2_up*GYsc
irf_s2_low  <- results_nl_iv$irf_s2_low*GYsc

results_nl_iv  <- list(irf_s1_mean  = irf_s1_mean,
                        irf_s1_up    = irf_s1_up,
                        irf_s1_low   = irf_s1_low,
                        irf_s2_mean  = irf_s2_mean,  
                        irf_s2_up    = irf_s2_up,
                        irf_s2_low   = irf_s2_low,
                        specs        = results_nl_iv$specs)
```


Make and save plots
```{r, message = FALSE }
 plots_nl_iv <- plot_nl(results_nl_iv)
 s1_plots    <- sapply(plots_nl_iv$gg_s1, ggplotGrob)
 s2_plots    <- sapply(plots_nl_iv$gg_s2, ggplotGrob)
```

This plot corresponds to the red dotted line in the lower panel (right plot) in Figure 12 in the Supplementary Appendix of RZ-18.
It shows the response of GDP to a shock in government spending equal to 1% of GDP during periods of economic expansions.
It is the same data, identification scheme and threshold definition as in AG-12 (see RZ-18). 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
 plot(plots_nl_iv$gg_s1[[3]])
```

This plot corresponds to the blue dotted line in the lower panel (right plot) in Figure 12 in the Supplementary Appendix of RZ-18.
It shows the response of GDP to a shock in government spending equal to 1% of GDP during periods of economic slack.
It is the same data, identification scheme and threshold definition as in AG-12 (see RZ-18). 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
 plot(plots_nl_iv$gg_s2[[3]])
```


## References
* Ahmed, M.I. , Cassou, S.C. (2016) "Does Consumer Confidence Affect Durable Goods Spending
During Bad and Good Economic Times Equally?" *Journal of Macroeconomics*, 50(1): 86-97.
[doi:10.1016/j.jmacro.2016.08.008](https://www.sciencedirect.com/science/article/pii/S0164070416300490)

* Auerbach, A. J., and Gorodnichenko Y. (2012). "Measuring the Output Responses to Fiscal Policy." *American Economic Journal: Economic Policy*, 4    (2):   1-27. [doi:10.1257/pol.4.2.1](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)

*  Auerbach, A. J., and Gorodnichenko Y. (2013). "Fiscal Multipliers in Recession and Expansion" *NBER Working Paper Series*. Nr 17447.  [National Bureau of Economic Research](http://www.nber.org/papers/w17447.pdf)

* Jordà, Ò. (2005) "Estimation and Inference of Impulse Responses by Local Projections." *American Economic Review*, 95 (1): 161-182.
[doi:10.1257/0002828053828518](https://www.aeaweb.org/articles?id=10.1257/0002828053828518)

* Jordà, Ò, Schularick, M., Taylor, A.M. (2015), "Betting the house", *Journal of International Economics*,
 96, S2-S18.

* Newey W.K., and West K.D. (1987). “A Simple, Positive-Definite, Heteroskedasticity and Autocorrelation Consistent Covariance Matrix.” *Econometrica*, 55: 703–708. [doi:10.2307/1913610](https://www.jstor.org/stable/1913610?seq=1#page_scan_tab_contents)

* Ramey, V.A., Zubairy, S. (2018). "Government Spending Multipliers in Good Times and in Bad: Evidence from US Historical Data." 
 *Journal of Political Economy*, 126(2): 850 - 901. [doi:10.1086/696277](https://www.journals.uchicago.edu/doi/10.1086/696277)

* Ravn, M.O., Uhlig, H. (2002). "On Adjusting the Hodrick-Prescott Filter for the Frequency of Observations."
  *Review of Economics and Statistics*, 84(2), 371-376.

### Author
Philipp Adämmer

### License

GPL (>= 2)
