---
output: html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "pics_docs/",
  fig.align = "center"
)
```


## Example: Estimate linear impulse responses
Load libraries:
```{r, message = FALSE }
  library(dplyr)
  library(doParallel)
  library(parallel)
  library(vars)
  library(Rcpp)
  library(lpirfs)
```

Load data from package to estimate a simple, new-Keynesian, closed-
economy model. These data are used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV, p. 174. 
See the data's help file or the [paper](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) for a detailed description. 
```{r, message = FALSE }
  data_set_df <- interest_rules_var_data
```

Make list and specify input variables to estimate linear impulse responses. 
```{r, message = FALSE }
# Make list for inputs
  specs <- list()

# Specify inputs
  specs$lags_lin       <- 4L      # Number of lags
  specs$lags_criterion <- NaN     # Lag length criterion (AICc, AIC or BIC)
  specs$max_lags       <- NaN     # If lags_criterion is chosen, set maximum number of lags  
  specs$trend          <- 0L      # 0 = no trend, 1 = trend, 2 = trend and quadratic trend
  specs$shock_type     <- 1L      # 0 = standard deviation shock, 1 = unit shock
  specs$confint        <- 1.96    # Width of confidence bands: 1 = 68%, 1.67 = 90%, 1.96 = 95%
  specs$hor            <- 24L     # Length of horizon
```
Estimate linear impulse responses with the package function *lp_lin*. Note that the VAR's endogenous variables (*data_set_df*) have to be 
a data.frame(). 
```{r, message = FALSE }  
  results_lin  <- lp_lin(data_set_df, specs)
```

Create plots for impulse responses of linear model with package function *plot_lin_irfs*.
```{r, message = FALSE }
  linear_plots <- plot_lin_irfs(results_lin)
```
Display single impulse responses: 

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable in (GDP_gap). 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (Inflation). 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
  linear_plots[[1]]
  linear_plots[[2]]
```

Display all plots (compare with Figure 5 in Jordà (2005), p. 176):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }  
# Load further libraries
  library(ggpubr)
  library(gridExtra)

# Show all plots 
  lin_plots_all <- sapply(linear_plots, ggplotGrob)
  marrangeGrob(lin_plots_all, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top=NULL)
```

## Example: Non-linear impulse responses
Load libraries:
```{r, message = FALSE }
  library(dplyr)
  library(doParallel)
  library(parallel)
  library(Rcpp)
  library(lpirfs)
  library(mFilter)
  library(vars)
```

Load data set from package to estimate a non-linear, new-Keynesian, closed-
economy model. These data are used by [Jordà (2005)](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) in chapter IV, p.176. 
See the data's help file or the [paper](https://www.aeaweb.org/articles?id=10.1257/0002828053828518) for a detailed description. 
```{r, message = FALSE }
  data_set_df <- interest_rules_var_data
```

Make list and specify input variables to estimate non-linear impulse responses. 
```{r, message = FALSE }
# Make list for inputs
  specs <- list()

# Specify inputs
  specs$lags_lin       <- 4L      # Number of lags for (reduced) linear VAR 
  specs$lags_nl        <- 4L      # Number of lags
  specs$lags_criterion <- NaN     # Lag length criterion (AICc, AIC or BIC)
  specs$max_lags       <- NaN     # If lags_criterion is chosen, maximum number of lags  
  specs$trend          <- 1L      # 0 = no trend, 1 = trend, 2 = trend and quadratic trend
  specs$shock_type     <- 0L      # 0 = standard deviation shock, 1 = unit shock
  specs$confint        <- 1.67    # Width of confidence bands: 1 = 68%, 1.67 = 90%, 1.96 = 95%
  specs$hor            <- 24L     # Length of horizon
```

Provide a switching variable to separate the data into two regimes.
```{r, message = FALSE }
# Specifications for switching variable
  specs$switching      <- data_set_df$Infl # Inflation rate
  specs$hp_filter      <- 1                # 0 = Do not use HP-filter to decompose switching-variable, 
                                           # 1 = Use HP-filter to decompose switching-variable
  specs$lambda         <- 1600             # Monthly = 129600, Quarterly = 1600, Annual = 6.25
  specs$gamma          <- 6                # Numeric value > 0
```

$$ $$
The switching variable ($z_t$) can either be decomposed by the Hodrick-Prescott filter (see [Auerbach and Gorodnichenko, 2013](http://www.nber.org/papers/w17447.pdf)) or directly plugged into the following transition function:  


 $$F({z_t})  = \  \frac{e^{(-\gamma z_t)}}{\left(1 + e^{(-\gamma z_t)})\right)},$$
 


where $\gamma > 0$. To differentiate between the two regimes, the exogenous variables ($\boldsymbol{y}_{t-p}$) are multiplied with the values of the transition function at *t − 1* where

- Regime 1 $(R_1)$: $\boldsymbol{y}_{t-i}\cdot(1-F(z_{t-1}))$,  $\qquad i = 1, ..., p$, and

- Regime 2 $(R_2)$: $\boldsymbol{y}_{t-i}\cdot F(z_{t-1})$,  $\hskip 4.5em i = 1, ..., p$.

 IMPORTANT: The index of $z$ is set to *t − 1* in order to avoid contemporaneous feedback (see 
[Auerbach and Gorodnichenko 2012](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)). 
The lag is automatically created in the package function *create_nl_data*. 
If you do not want the exogenous variables to be multiplied with lagged values of $F({z_t})$, you have to provide the switching variable with a lead of one.

Non-linear impulses responses are computed as in [Ahmed and Cassou (2016)](https://www.sciencedirect.com/science/article/pii/S0164070416300490). 
First, a reduced VAR is estimated to obtain the covariance matrix of the residuals $\Sigma$. The Cholesky decomposition is then applied to obatin the shock matrix with columns denoted by $d_i$. IRFs for both regimes are estimated via:

$$\hat{IR}^{R_1}(t,h,d_i) = \hat{\boldsymbol{B}}_{1, R_1}^h d_i, \ \ \ \ \ \ \ \ \ h = 1, ..., H, $$ 
and 

$$\hat{IR}^{R_2}(t,h,d_i) = \hat{\boldsymbol{B}}_{1, R_2}^h d_i, \ \ \ \ \ \ \ \ \ h = 1, ..., H, $$ 


with $\hat{\boldsymbol{B}}_{1, R1}^0 = I$ and $\hat{\boldsymbol{B}}_{1, R1}^0 = I$. The parameters are obtained by running a sequence of OLS forecasts (local projections):

$$ \boldsymbol{y}_{t+h} = \boldsymbol{\alpha}^h + \boldsymbol{B}_{1, R_1}^{h} \left(\boldsymbol{y}_{t-1}\cdot(1-F(z_{t-1})\right) \ + \ ...\ +\ 
    \boldsymbol{B}_{p, R_1}^{h} \left(\boldsymbol{y}_{t-p}\cdot(1-F(z_{t-1})\right) + \\
\boldsymbol{B}_{1, R_2}^{h} \left(\boldsymbol{y}_{t-1}\cdot F(z_{t-1}\right)) \ + \ ... \  + \  \boldsymbol{B}_{p, R_2}^{h} \left(\boldsymbol{y}_{t-p}\cdot F(z_{t-1}\right)) + \boldsymbol{\varepsilon}_{t+h}^h,
$$
with $h = 1,..., H.$

$$ $$

Estimate non-linear impulse responses with package function *lp_nl*. Note that the VAR's data set (*data_set_df*) has to be 
a data.frame(). 
```{r, message = FALSE }  
  results_nl <- lp_nl(data_set_df, specs)
```

Save values from transition function.
```{r, message = FALSE } 
  fz      <- results_nl$fz
```

Plot output gap
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE } 
# Make date sequence and store data in data_frame.
  dates   <- seq(as.Date("1955/12/1"), as.Date("2003/1/1"), by = "quarter")
  data_df <- data_frame(x = dates, fz = fz, gdp_gap = specs$switching[(specs$lags_nl+1):length(data_set_df$FF)])

# Plot  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = gdp_gap)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```

Plot transition function
```{r, fig.height = 4, fig.width = 6, fig.align = "center", message = FALSE }  
  ggplot(data = data_df) +
    geom_line(aes(x = x, y = fz)) +
    theme_bw() +
    ylab("") +
    xlab("Date") +
    scale_x_date(date_breaks = "5 year",  date_labels = "%Y")
```

Create and save all plots with package function *plot_nl_irfs*
```{r, message = FALSE }
    nl_plots <- plot_nl_irfs(results_nl)
```

Show single impulse responses for each regime:

- The first plot shows the response of the first variable (GDP_gap) to a shock in the first variable (GDP_gap) in regime 1. 
- The second plot shows the response of the first variable (GDP_gap) to a shock in the second variable (Inflation) in regime 2. 
```{r, fig.height = 2.5, fig.width = 3, fig.align = "center", message = FALSE }
# Load packages
  library(ggpubr)
  library(gridExtra)

# Save plots based on states
  s1_plots <- sapply(nl_plots$gg_s1, ggplotGrob)
  s2_plots <- sapply(nl_plots$gg_s2, ggplotGrob)

  plot(s1_plots[[1]])
  plot(s2_plots[[2]])
```

Show all impulse responses of regime 1 (high inflation rates):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s1_plots, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top =  NULL)
```

Show all impulse responses of regime 2 (low inflation rates):
```{r, fig.height = 6, fig.width = 8, fig.align = "center", message = FALSE }
  marrangeGrob(s2_plots, nrow = ncol(data_set_df), ncol = ncol(data_set_df), top = NULL)
```


## References
* Ahmed, M.I. , Cassou, S.C. (2016) "Does Consumer Confidence Affect Durable Goods Spending
During Bad and Good Economic Times Equally?" *Journal of Macroeconomics*, 50(1): 86-97.
[doi:10.1016/j.jmacro.2016.08.008](https://www.sciencedirect.com/science/article/pii/S0164070416300490)

* Auerbach, A. J., and Gorodnichenko Y. (2012). "Measuring the Output Responses to Fiscal Policy." *American Economic Journal: Economic Policy*, 4    (2):   1-27. [doi:10.1257/pol.4.2.1](https://www.aeaweb.org/articles?id=10.1257/pol.4.2.1)

*  Auerbach, A. J., and Gorodnichenko Y. (2013). "Fiscal Multipliers in Recession and Expansion" *NBER Working Paper Series*. Nr 17447.  [National Bureau of Economic Research](http://www.nber.org/papers/w17447.pdf)

* Jordà, O. (2005) "Estimation and Inference of Impulse Responses by Local Projections." *American Economic Review*, 95 (1): 161-182.
[doi:10.1257/0002828053828518](https://www.aeaweb.org/articles?id=10.1257/0002828053828518)

* Newey W.K., and West K.D. (1987). “A Simple, Positive-Definite, Heteroskedasticity and Autocorrelation Consistent Covariance Matrix.” *Econometrica*, 55: 703–708. [doi:10.2307/1913610](https://www.jstor.org/stable/1913610?seq=1#page_scan_tab_contents)


### Author
Philipp Adämmer

### License

GPL (>= 2)
